---
title: "Homework Exercise #1"
author: "Name"
date: "`r Sys.Date()`"
output: pdf_document
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyfoot{}
  - \fancyhead[R]{309.716.01}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
```

## Instructions

For this assignment, you will perform multiple regression analyses using the variable **total expenditures (totexp08)**, regressed on **age (as of the end of the year)**, **female**, **Census region**, **family income as a percent of the poverty line**, and **years of education** when first entered MEPS.

Data Preparation:

 + Sample: Include only adults aged 18 and older.
 + Treat years of education as a continuous variable.

**Important**: For this homework, we are not going to take survey structure into account. 

Please ensure that your analyses and results are clearly presented, well-documented, and logically justified. If you have any questions or need clarification on any part of the assignment, feel free to reach out for assistance.

## Q1: Descriptive Statistics

```{r q1}
```

 a) How many observations do you have with non-missing values for total expenditures?
 b) Identify which variable(s) have missing observations and specify how many observations are missing for each variable.
